\documentclass{article}

\usepackage{fullpage}
\usepackage{parskip}

\begin{document}

\begin{center}
\Huge{Immediate Feedback on Project Presentation}\\
\end{center}


\normalsize
\textbf{Company name:}\\

Axiom Enterprise \\

\textbf{Content: 70}\\

This is perhaps the weakest part of your work.
You (understandably) spent a lot (most?) of your presentation talking about the code without spending enough time on the specifics of the problem, the market research etc...

I believe that this is simply because you had worked so hard on the code and wanted to talk about it.
I understand.\\

\textbf{Code: 100}\\

Off the scale completely compared to everyone else.

I (incorrectly) had assumed from your minutes that Alex was the main coder and other members of the group were working on other things (this has been the case for a lot of groups).
This was obviously not quite right so it's really nice to see that you all worked so hard on the code and learnt git as well.

Huge congratulations on the code gentlemen.
There are things you have done that I would appreciate you teaching me.\\

\textbf{Delivery: 79}\\

Excellent delivery.
As I said at the time, you could perhaps employ a head of sales to help get your message across to a non-coding audience but you guys presented what you did \textbf{very} well.

A pleasure to listen to.\\

\textbf{Visual Aids: 80}\\

Good use of visual aids.

\textbf{Creativity: 96}\\

Very creative: well done!\\


\textbf{General comments}\\

Ridiculous piece of code for an 11 week project guys.

Absolutely brilliant, your enthusiasm for it was really nice to see as well.

A personal thank you for your efforts and engagement.

I encourage you to keep working on this.\\

\textbf{Overall Mark: 85/100}

\end{document}
