\documentclass{article}

\usepackage{fullpage}
\usepackage{parskip}

\begin{document}

\begin{center}
\Huge{Immediate Feedback on Project Presentation}\\
\end{center}


\normalsize
\textbf{Company name:}\\

$\frac{dy}{dx}$ \\

\textbf{Content: 100}\\

I would like to personally thank you for your engagement and efforts in this project.
You carried out an extremely strong market research and had a huge quantity of ideas.\\

On a critical level, I thought the production levels for your play were poor.
Lighting could have been better as well as the use of more complex visual effects.
A car chase would have improved the overall tempo of the play.\\

(To clarify: that is meant as a joke: I \textbf{loved} the play!, I'll talk about the song somewhere else at some point...)\\

\textbf{Code: 97}\\

Well done!
Great use of wx and overall strong level of coding.
Nice that everything was object based.\\

\textbf{Delivery: 100}\\

Excellent: you obviously prepared very well for this.
Well done to everyone!

Tomos you are obviously extremely comfortable in front of a crowd.
You come across in a very likeable way and your enthusiasm for the project was evident.

The song more or less was a killer feature to the whole thing.
Most entertaining talk to sit through.

Thank you.\\

\textbf{Visual Aids: 100}\\

Great: did a good job.\\

\textbf{Creativity: 100}\\

\textbf{Very, very} creative.\\

\textbf{General comments}\\

Excellent presentation and good work on the project itself.\\

Your next step is to look at kivy and get that working.
I'd be delighted to help you guys take this further if I can.

\textbf{Overall Mark: 99/100}

\end{document}
