\documentclass{article}

\usepackage{fullpage}
\usepackage{parskip}

\begin{document}

\begin{center}
\Huge{Immediate Feedback on Project Presentation}\\
\end{center}


\normalsize
\textbf{Company name:}\\

Easy as $\pi$ \\

\textbf{Content: 90}\\

Great idea!
Perhaps at times though your idea got lost a bit throughout.\\

\textbf{Code: 70}\\

The code used is appropriate yet basic.
Well done on learning something new.\\

\textbf{Delivery: 95}\\

Da iawn.
Siaradoch chi gyd yn wych, ac roedd yn bleser i wrando ar.
As an audience we had no choice but to listen to you as you each had a great way of hooking the audience with your presence and voice.

You were all dressed smartly and seemed well organised.
If I'm being picky one way this could have been better is if you had no notes although you read from the notes well with plenty of eye contact.
Again though, that's being picky, your \textbf{presence} was second to none.\\

\textbf{Visual Aids: 65}\\

This could have been slightly better.
At times when you were talking about complicated concepts you did not have visual aids to complement and `aid' you.
Your vocal delivery is absolutely brilliant so next time just try and think about what you can have on a screen to complement that.

\textbf{Creativity: 78}\\

Good idea.\\


\textbf{General comments}\\

Very nice idea and extremely well presented.
I would encourage you to take this further and if I can assist you to do so please don't hesitate to ask.\\

\textbf{Overall Mark: 80/100}

\end{document}
