\documentclass{article}

\usepackage{fullpage}
\usepackage{parskip}

\begin{document}

\begin{center}
\Huge{Immediate Feedback on Project Presentation}\\
\end{center}


\normalsize
\textbf{Company name:}\\

Edumath \\

\textbf{Content: 100}\\

I would like to personally thank you for your engagement and efforts in this project.
You all worked very well together and considered all the important aspects.
You should be proud of what you have accomplished.\\

\textbf{Code: 100}\\

Well done!
You not only learnt something new (kivy) \textbf{but} you learnt it well!
It seemed that the coding aspect of this work was mainly taken care of by Timothy (which is not a problem in my eyes: everyone has their strengths).
I would suggest that perhaps Timothy could try (if this has not already happened) to give everyone a quick explanation of some of the concepts (for your own benefit).\\

Next year some students will most probably use kivy for their project.
Timothy I would be very appreciative if you could perhaps put together some resources (videos, handouts etc...) to support them that would be great.
This is something we can talk about at a later date.
It could be something that you and I work on together during code club session next year.\\

\textbf{Delivery: 100}\\

Great job guys, you were well prepared and came across very well.
The humour/teasing of me was brilliant, but (this is meant to be helpful advice) be sure to know your audience when trying this in the future.
Others might not approve and a 100\% professional approach might at times be more appropriate.
In this instance you knew your audience well and it wasn't at all a problem.
You all presented very well although this is (if I'm being extremely picky and once again trying to be helpful) something that Timothy wasn't as comfortable with as everyone else.
Timothy you still did a great job but this is something that you could personally work on slightly. (I am being extremely picky here).\\


\textbf{Visual Aids: 100}\\

Great use of Visual aids, the videos were not \textit{too much} and helped.
The flyers were awesome and the app looked great on the screen: good job everybody.\\

\textbf{Creativity: 100}\\

Awesome job, the app is a great idea and your idea to target parents was very well thought out and justified.\\

\textbf{General comments}\\

Brilliant job guys, I would be delighted to help you push this further.
Let me know what I can do.\\

I hoped you enjoyed working on this as much as myself and Athena enjoyed listening to your presentation.\\

You came across as a close team: nice to see.\\

\textbf{Overall Mark: 100/100}

\end{document}
