\documentclass{article}

\usepackage{fullpage}
\usepackage{parskip}

\begin{document}

\begin{center}
\Huge{Immediate Feedback on Project Presentation}\\
\end{center}


\normalsize
\textbf{Company name:}\\

Kade \\

\textbf{Content: 90}\\

Well done on putting together a strong product.
I don't believe there's anything out there like this and I think if done properly could be great!
Your market analysis was strong and well done on going out and talking to taxi firms and the student Union.\\

\textbf{Code: 100}\\

Excellent job learning Kivy and using the shap.py library.

Next step really is to get the gmaps working...
You can certainly either wait for someone to get the package working \textbf{OR} sort it yourselves.
I'd be delighted to help.\\

\textbf{Delivery: 90}\\

Excellent: you obviously prepared very well for this.
Well done to everyone!

At one point you answered questions that you had actually answered in your talk.
You did this in a great way: you just answered the question and did not point out that you had already addressed this.
Some people often say `as I said before...' this come across poorly.
Well done for not doing that.\\

\textbf{Visual Aids: 90}\\

Great: the app looked great.
It would be worth making your logo a bit better: read up on what are called vector graphics and take a look at a piece of software called inkscape.\\

\textbf{Creativity: 90}\\

Very creative: well done!\\


\textbf{General comments}\\

Excellent presentation and good work on the project itself.\\

I really encourage you to take this further guys, as well as the app I think you want to start working on a basic website as well as an explanatory video perhaps?

I'd be delighted to help if I can.\\

\textbf{Overall Mark: 92/100}

\end{document}
