\documentclass{article}

\usepackage{fullpage}
\usepackage{parskip}

\begin{document}

\begin{center}
\Huge{Immediate Feedback on Project Direction}\\
\tiny{(This is some feedback to make sure your project is on the right track: you will be given detailed a mark and detailed feedback asap.)}
\end{center}


\normalsize
\textbf{Company name:}\\

Abacus \\

\textbf{Technical aspects:}\\

The big thing missing from your report is details with regards to how you will actually build your website.

If/when this is actually going to go live you will want a robust web framework like Django.
This might be difficult for you to grasp in the amount of time you have available to you but take a look at Pythonanywhere.com which might be helpful and/or come and see me.
With regards to a forum take a look at Disqus.com but this won't help with the mathematics (which could actually end up being your USP). You'll want to take a look at Mathjax.

All of the above could be done using Django (and this would indeed be \textbf{the} way to do it properly).
Realistically though you might not be able to do this with the time you have left but remember that your pitch must include code so you might want to investigate some javascript (a light language that can be interpreted by a browser). \textbf{Just html will not get you any marks for code.} If any of the above is unclear come and speak to me.

\textbf{Initial comments about write up:}\\

The write up is extremely well written: good job!
If possible I would like to use this write up as a showcase for future years (if you don't mind)\\

\textbf{Initial comments about strategy:}\\

Well thought out strategy with some excellent market research (well done on getting the focus group involved).
You could have asked them more questions though, for example do they agree with you that the websites out there are not appealing?\\

\textbf{General comments}\\

Good job, great idea just now concentrate on the technical aspects as well as fine tuning certain strategy details.

\end{document}
