\documentclass{article}

\usepackage{fullpage}
\usepackage{parskip}

\begin{document}

\begin{center}
\Huge{Immediate Feedback on Project Direction}\\
\tiny{(This is some feedback to make sure your project is on the right track: you will be given detailed a mark and detailed feedback asap.)}
\end{center}


\normalsize
\textbf{Company name:}\\

Ausfall. \\

\textbf{Technical aspects:}\\

Technically this project sounds devoid of content.

What you are suggesting is basically 1 line of Sage code (potentially two lines of Python code).

Also you mention Wolfram alpha so my main question is why would anyone use your product given that Wolfram Alpha can be used?

If you plan on building the site itself (so as to actually have some technical content) then you have a lot of work to do to familiarise yourselves with how to do that.\\

\textbf{Initial comments about write up:}\\

Poorly written, with opinions offered as facts and various things clumsily repeated. This feels like very little effort has gone in to it.

\textbf{Initial comments about strategy:}\\

I don't think there is a need for your product and secondly I don't see anything innovative in it.

Your job is to justify that my assessment is incorrect, not through opinion but through market research.

What you have called Market research is just a small review of Wolfram Alpha that I'm not sure your product would `beat'.

Finally as a teaching tool I would much rather my students used something that taught them how to code although I'm not entirely sure what your product actually is (a part from a line of Sage code) so perhaps I am misunderstanding.

\textbf{General comments}\\

Much more thorough market research must be carried out and you need to think about the technical aspects of your product.

\end{document}
